\chapter{Model description}
\label{ch:model-description}

In this chapter, we motivate why the models were selected and 
describe their basic functionality as well as their advantages.

Quantile Regression Forests have proven to be a very competitive 
and powerful quantile regression method for high-dimensional datasets. 
Quantile Regression Forests were used by three of the top five contestants 
in the solar energy track in the GEFCom2014 challenge (cf. \Textcite{Hong2016}, Table 11). 
There are also multiple libraries that implement Quantile Regression Forests.
Therefore, they do not only perform 
well but they are also simple to implement as a benchmark.
This is the reason why we use it as a competitive benchmark model.
Nearest Neighbor Quantile Regression is the method utilized by the first place 
in the GEFCom14 challenge. \Textcite{Ordiano2019} claim that NNQF uses a similar strategy but requires much less 
computation power in order to predict its output. 
\Textcite{Gasthaus2019} explain that SQF-RNN uses autoregressive input with an RNN structure and provides flexible 
conditional output distributions through spline quantile functions. 
They also show that it works well on large solar energy 
forecasting datasets.

In order to describe the model in the following subsections, we will introduce the necessary notation here:
\begin{itemize}
    \item \(n\) is the training data length
    \item \(x_1, \ldots, x_n \in \R^D\) are the predictor values of the time series
    \item \(y_1, \ldots, y_n \in \R\) are the corresponding target values
\end{itemize}

\input{sections/model-description/description-qrf}

\input{sections/model-description/description-nnqf}

\input{sections/model-description/description-sqf-rnn}