\section{The GEFCom2014 dataset}

In order to compare different energy forecasting methods, 
\Textcite{Hong2016} organized the Global Energy Forecasting Competition 2014 (GEFCom2014), 
a probabilistic energy forecasting competition with four tracks: 
electric load, electric price, wind power and solar power forecasting. 
The competition attracted 581 participants from 61 countries. 

The Global Energy Forecasting Competition took place the first time in 2012. 
In the 2014 competition, they upgraded the competition with three features: 
\begin{enumerate}
    \item instead of point forecasts, probabilistic forecasts were used;
    \item four forecasting tracks were used: electric load (L track), 
    electric price (P track), wind power (W track) and solar power (S track);
    electric load an wind forecasting were also used in 2012, solar power and 
    electric price forecasting were added;
    \item incremental data releases on a weekly basis to mimic real world forecasting.
\end{enumerate}

In this thesis, we will only look at the solar power track. 
In this track, you need to predict the power generation of three 
solar power plants (the so called zones) in Australia. 
The prediction should be on a rolling basis for \(\SI{24}{\hour}\) ahead. 
For the forecasts, you get different prediction variables shown in Table \ref{table:predictors}.

\begin{table}[ht]
\caption{Predictors for the GEFCom2014-S track \\ Adapted from Table 10 in \cite{Hong2016}}
\label{table:predictors}
\rowcolors{2}{white}{gray!25}
\footnotesize
\begin{tabularx}{\textwidth}{llX}
    \toprule
    \tableheads Variable name & \tableheads Units & \tableheads Comments \\
    \midrule
    Total column liquid water (tclw) & \(\si{\kilo\gram\per\square\metre}\) & Vertical integral of cloud liquid water content \\
    Total column ice water (tciw) & \(\si{\kilo\gram\per\square\metre}\) & Vertical integral of cloud ice water content \\
    Surface pressure (SP) & \(\si{\pascal}\) & \\
    Relative humidity at \(\SI{1000}{\milli\barsi}\) (r) & \(\%\) & Relative humidity is defined with respect to saturation of
                                                                  the mixed phase, i.e., with respect to saturation over ice
                                                                  below \(\SI{-23}{\degreeCelsius}\) and with respect to saturation over water 
                                                                  above \(\SI{0}{\degreeCelsius}\). In the regime in between, a quadratic
                                                                  interpolation is applied. \\
    Total cloud cover (TCC) & \(0\)-\(1\) & TCC derived from model levels using the
                                            model's overlap assumption \\
    \(10\)-metre \(U\) wind component (\(10u\)) & \(\si{\metre\per\second}\) & \\
    \(10\)-metre \(V\) wind component (\(10v\)) & \(\si{\metre\per\second}\) & \\
    \(2\)-metre temperature (\(2T\)) & \(\si{\kelvin}\) & \\
    Surface solar rad down (SSRD) & \(\si{\joule\per\square\metre}\) & Accumulated field \\
    Surface thermal rad down (STRD) & \(\si{\joule\per\square\metre}\) & Accumulated field \\
    Top net solar rad (TSR) & \(\si{\joule\per\square\metre}\) & Net solar radiation at the top of the atmosphere. Accumulated field \\
    Total precipitation (TP) & \(\si{\metre}\) & Convective precipitation \(+\) stratiform precipitation (CP + LSP). Accumulated field \\
    \bottomrule
\end{tabularx}
\end{table}

\subsection{Error measure}

To evaluate the different forecast competitors in GEFCom2014, 
the pinball loss was used -- mainly because of the ease of implementation 
and because the pinball loss is a proper scoring rule (see \ref{sec:proper-scoring-rules}).
For each time period over the forecast horizon, the participants need to 
provide the quantiles \(q_{0.01}, \ldots, q_{0.99}\). 
\(q_0 = -\infty\) and \(q_1 = \infty\) are the natural lower and upper bounds. 
Those quantiles are then evaluated with the pinball loss (see \ref{sec:pinball-loss}).

The overall score is the average over all time points, zones and quantiles.
The models are then compared with a benchmark which is a basic point forecast 
that was created using a na\"{i}ve model.